Score-based tests of measurement invariance: Use in practice

### 2013-10-02 frontiers/frontiers.Rnw
update frontier.Rnw file according to Ed's comment. Change formate etc.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@271 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

To examine these specificity issues, we generated data from a
two-factor model with three indicators each (see Figure~\ref{fig:path}).
The measurement invariance
violation occurred in one of three places: the factor loading associated with Scale 1 
 ($\lambda_{11}$), the unique variance associated with Scale 1
 ($\psi_{11}$), or the factor covariance $\sigma_{12}$.  
\readme{Isn't this five subsets of parameters, not seven?}
 We then tested for measurement invariance in seven subsets of parameters: the three
individual parameters noted above, all six factor loadings, % $\lambda_{11}--\lambda_{62}$, and 
and all six unique variances. % $\epsilon_{11}--\epsilon_{66}$.

@@

\readme{Make sure there is a space after each comma and period:}
In summary, the proposed test statistics appear robust to unmodeled loading parameters,so long
as the umodeled parameter does not violate measurement invariance. If the unmodeled parameter 
dose violate measurement invariance, however, then the tests assign this violation to other 
parameters that do not violate measurement invariance. The impacted parameters include the error
variance and other loadings associated with the manifest variables that had the unmodeled 
loading. Thus, as it is with other tests of measurement invariance, it is important to study the extent to
which the hypothesized model includes all parameters of importance.

>>>>

To examine these specificity issues, we generated data from a
two-factor model with three indicators each (see Figure~\ref{fig:path}).
The measurement invariance
violation occurred in one of three places: the factor loading associated with Scale 1 
 ($\lambda_{11}$), the unique variance associated with Scale 1
 ($\psi_{11}$), or the factor covariance $\sigma_{12}$.  
 We then tested for measurement invariance in five subsets of parameters: the three
individual parameters noted above, all six factor loadings, % $\lambda_{11}--\lambda_{62}$, and 
and all six unique variances. % $\epsilon_{11}--\epsilon_{66}$.

@@

In summary, the proposed test statistics appear robust to unmodeled loading parameters, so long
as the umodeled parameter does not violate measurement invariance.  If the unmodeled parameter 
dose violate measurement invariance, however, then the tests assign this violation to other 
parameters that do not violate measurement invariance.  The impacted parameters include the error
variance and other loadings associated with the manifest variables that had the unmodeled 
loading.  Thus, as it is with other tests of measurement invariance, it is important to study the extent to
which the hypothesized model includes all parameters of importance.
